Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-29 manuscript/manuscript.tex
Fix British spelling for modelling

An application to modeling the Neuqu\'en Basin, Argentina, demonstrates that the effects
of sediment compaction cannot be ignored.
When compared to an exponential density function, a homogeneous density with depth would
result in an error of up to -8 mGal, while a linear density function would result in up
to -6 mGal error.
Accurate and robust forward modeling is a key component to any gravity inversion method.
Errors of this magnitude could result in significant overestimation of sedimentary
basin thickness, for example.

>>>>

An application to modelling the Neuqu\'en Basin, Argentina, demonstrates that the
effects of sediment compaction cannot be ignored.
When compared to an exponential density function, a homogeneous density with depth would
result in an error of up to -8 mGal, while a linear density function would result in up
to -6 mGal error.
Accurate and robust forward modelling is a key component to any gravity inversion
method.
Errors of this magnitude could result in significant overestimation of sedimentary
basin thickness, for example.
